Hyperopt-Sklearn: Subtitle?

### 2014-04-26 papers/2014-automl/paper.tex
paper captions and future work

\begin{figure}
    \centering
    \includegraphics[width=2.9in]{graphics/scores_by_classifier}
    \includegraphics[width=2.9in]{graphics/scores_per_eval}
    \caption{
	    XXX
    }
    \label{fig:per_clf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3in]{graphics/AvgMinValidErrorTPE}
    \caption{
	    XXX
    }
    \label{fig:errtpe}
\end{figure}

@@

\section{Discussion and Future Work}
Future Work
Lots of areas for future work:
Speed: Aborting points early when using K-fold validation
Applications: Extending search space for e.g. regression problems
Input domains: Including more pre-processing to handle different kinds of data

>>>>

\begin{figure}
    \centering
    \includegraphics[width=4.5in]{graphics/scores_by_classifier}
    %\includegraphics[width=2.9in]{graphics/scores_per_eval}
    \caption{
	    Using Hyperopt's Anneal search algorithm, increasing the number of function evaluations from 150 to 2400 lead to a modest improvement in accuracy on 20 Newsgroups and MNIST,
        and a more dramatic improvement on Convex Shapes.
        We capped evaluations to 5 minutes each so 300 evaluations took between 12 and 24 hours of wall time.
    }
    \label{fig:per_clf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3in]{graphics/AvgMinValidErrorTPE}
    \caption{
        Hyperopt's TPE algorithm makes gradual progress on 20 Newsgroups over 300 iterations and gives no indication of convergence.
        We look forward to investigating alternative optimization algorithms in future work.
    }
    \label{fig:errtpe}
\end{figure}

@@

\section{Discussion and Future Work}
Hyperopt-sklearn provides many opportunities for future work.
Certainly, there are more classifiers and preprocessing modules that could be included in the search space,
and there are more ways to combine even the existing components.
In expanding the search space, care must be taken to ensure that the benefits of new models outweigh the greater difficulty of searching a larger space.

We have shown here that Hyperopt's random search, annealing search, and TPE algorithms make Hyperopt-sklearn viable, but the slow convergence in e.g. Figure~\ref{fig:errtpe} suggests
that other optimization algorithms might be more call-efficient.
The development of Bayesian optimization algorithms is an active research area, and  we look forward to looking at how other search algorithms interact with hyperopt-sklearn's search spaces.

Computational wall time spent on search is of great practical importance, and hyperopt-sklearn currently spends a significant amount of time evaluating points that are un-promising.
Techniques for recognizing bad performers early could speed up search enormously.
Relatedly, hyperopt-sklearn currently lacks support for K-fold cross-validation. In that setting, it will be crucial to follow SMAC in the use of racing algorithms to skip un-necessary folds.

Another direction for future work is the extention of the techniques presented here in terms of classification to other types of machine learning problems (e.g. regression, density estimation, and ranking),
and other types of input modalities (e.g. large images, sound, timeseries, preferences).
